### 2021-07-10 src/paper/data/rapid_test_demand.tex

According to the COSMO study \citep{Betsch2021a} 63\% would have been willing to take a
test in the round of 23rd of February 2021 when an acquaintance would have tested
positive. Since this is only asking for willingness not actual behavior and the demand
when meeting with friends is very likely lower, we take this as the upper bound of
private rapid test demand which is reached in the beginning of May. To cover that many
people are likely to have sought and done their first rapid test before the Easter
holidays to meet friends or family, we let the share of individuals doing rapid tests in
that time increase more rapidly than before and after. By end of March 25\% of
individuals would do a rapid test due to a private reason.

>>>>

According to the COSMO study \citep{Betsch2021a} 63\% would have been willing to take a
test in the round of 23rd of February 2021 when an acquaintance would have tested
positive. Since this is only asking for willingness not actual behavior, we take this as
the upper bound of private rapid test demand which is reached in the beginning of May. To
cover that many people are likely to have sought and done their first rapid test before
the Easter holidays to meet friends or family, we let the share of individuals doing
rapid tests in that time increase more rapidly than before and after. By end of March
25\% of individuals would do a rapid test due to a private reason.

All shares of individuals who would take a rapid test if the conditions were met can be
seen in Figure~\ref{fig:rapid_test_demand}.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/data/testing/rapid_test_demand_shares}
    \caption{Share of Individuals Doing a Rapid Test.}
    \floatfoot{\noindent \textit{Note:} Rapid test demand can be triggered by individuals
    planning to have education contacts, work contacts, developing symptoms without
    access to a PCR test, having a household member with a positive test or symptoms. In
    each case whether a rapid test is done depends on how long it has been since the
    individual's last rapid test and her individual compliance parameters. As an example,
    take a worker in May. In that time workers are encouraged to test themselves twice
    weekly but there is no general requirement to test themselves. If the worker has not
    done a test within the last four days in our model she will demand a test if her
    (time-constant) compliance parameter belongs to the upper 60\% in the population.}
    \label{fig:rapid_test_demand}
\end{figure}

\FloatBarrier

### 2021-07-10 src/paper/data/share_known_cases.tex

One important feature of our model is that we distinguish between undetected and detected
cases and that we model which cases are detected and which are not (see \ref{sub:testing}
for a detailed description for how we model both rapid and PCR tests). For our model it
is important to have an estimate for the share of cases that is detected in the absence
of rapid tests. For this we rely on the
\href{https://covid19.dunkelzifferradar.de/}{Dunkelzifferradar} which relies on estimates
of the case fatality rate to estimate the number of total cases given the number of
deaths which are suspected to be perfectly observable. For 2020, we follow the reported
share of detected cases quite closely only interpolating the phase of November 2020 where
the testing policy was changed to give more priority to vulnerable groups. This lead to
more tests being done among older age groups which are also at the highest risk of dying
from CoViD-19 and an overestimation of the share of detected cases.
% After Christmas 2020
Similarly, the start of vaccinations after Christmas 2020 that were predominantly given
to nursing homes in the beginning and other vulnerable groups in spring, led to a
decrease in the number of deadly cases, leading to an increasing upward bias in the share
of detected cases. This is why we stop using the Dunkelzifferradar after Christmas.
Instead, we assume that that the share of detected cases would have stayed the same in
the absence of rapid tests. Thus, we also achieve in our model an increase in the share
of detected cases but this is driven from inside our model through increased testing and
follow-ups on positive rapid tests (see Section~\ref{subsec:results_share_known_cases}).
% Christmas and Easter
Lastly, we include reductions in the share known cases due to the two major holidays in
our simulation period, Christmas and Easter. During both holidays where many laboratories
do not process tests and most physicians' offices are closed, less PCR tests were done
leading to short and large drops in the share of known cases.

>>>>

One important feature of our model is that we distinguish between undetected and detected
cases and that we model which cases are detected and which are not (see
Section~\ref{sub:testing} for a detailed description for how we model both rapid and PCR
tests). For our model it is important to have an estimate for the share of cases that is
detected in the absence of rapid tests. For this we rely on the
\href{https://covid19.dunkelzifferradar.de/}{Dunkelzifferradar} which relies on estimates
of the case fatality rate to estimate the number of total cases given the number of
deaths which are suspected to be perfectly observable. For 2020, we follow the reported
share of detected cases quite closely only interpolating the phase of November 2020 where
the testing policy was changed to give more priority to vulnerable groups. This lead to
more tests being done among older age groups which are also at the highest risk of dying
from CoViD-19 and an overestimation of the share of detected cases.% After Christmas 2020
Similarly, the start of vaccinations after Christmas 2020 that were predominantly given
to nursing homes in the beginning and other vulnerable groups in spring, led to a
decrease in the number of deadly cases, leading to an increasing upward bias in the share
of detected cases. This is why we stop using the Dunkelzifferradar after Christmas.
Instead, we assume that that the share of detected cases would have stayed the same in
the absence of rapid tests. Thus, we also achieve in our model an increase in the share
of detected cases but this is driven from inside our model through increased testing and
follow-ups on positive rapid tests (see Section~\ref{subsec:results_share_known_cases}).
% Christmas and Easter
Lastly, we include reductions in the share known cases due to the two major holidays in
our simulation period, Christmas and Easter. During both holidays where many laboratories
do not process tests and most physicians' offices are closed, less PCR tests were done
leading to short and large drops in the share of known cases.

### 2021-07-10 src/paper/model/testing.tex

While rapid tests do not directly enter official case numbers, many positively tested
individuals confirm their rapid test result with a PCR test.\comment[id=J]{Need to link
to data appendix once the number is there and maybe mention the number}. Importantly,
those PCR tests are made in addition to the tests that would have been done otherwise.
Section~\ref{subsec:appendix_share_known_cases} discusses the effect of rapid tests on
the share of detected cases.

>>>>

While rapid tests do not directly enter official case numbers, many positively tested
individuals confirm their rapid test result with a PCR test.\comment[id=J]{Need to link
to data appendix once the number is there and maybe mention the number}. Importantly,
those PCR tests are made in addition to the tests that would have been done otherwise.
Section~\ref{subsec:results_share_known_cases} discusses the effect of rapid tests on
the share of detected cases.\comment[id=K]{Talk here about reactions to tests and
symptoms with contact reductions. (If not here, find other place where to talk about this
in detail.)}

### 2021-07-10 src/paper/report.tex

The model is applied to the second and third waves of the CoViD-19 pandemic in Germany,
covering the period mid-September 2020 to the end of May 2021.
Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and
of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially
recorded cases; the black line in Figure~\ref{fig:stringency_infectious_contacts} the
Oxford Response Stringency Index \citep{Hale2020}, which tracks the tightness of
non-pharmaceutical interventions. The index is shown for illustration of the NPIs, we
never use it directly. For legibility reasons, we transform the index so that lower
values represent higher levels of restrictions. A value of zero means all measures
incorporated in the index are turned on. The value 1 represents the situation in
mid-September, with restrictions on gatherings and public events, masking requirements,
but open schools and workplaces. In the seven weeks between mid September and early
November, cases increased by a factor of 10. Restrictions were somewhat tightened in
mid-October and again in early November. New infections remained constant throughout
November before rising again in December, prompting the most stringent lockdown to this
date. Schools and daycare centers were closed, so were customer-facing businesses except
for grocery and drug stores. From the peak of the second wave just before Christmas
until the trough in mid-February, newly detected cases decreased by almost three
quarters. The third wave in the spring of 2021 is associated with the B.1.1.7 strain,
which became dominant in March (Figure~\ref{fig:share_b117}). In early March, some NPIs
were being relaxed; e.g., hairdressers and home improvement stores were allowed to open
again to the public. There were many changes in details of regulations afterwards, but
they did not change the overall stringency index.

>>>>

The model is applied to the second and third waves of the CoViD-19 pandemic in Germany,
covering the period mid-September 2020 to the end of May 2021.
Figure~\ref{fig:pandemic_drivers_model_fit} describes the evolution of the pandemic and
of its drivers. The black line in Figure~\ref{fig:aggregated_fit} shows officially
recorded cases; the black line in Figure~\ref{fig:stringency_infectious_contacts} the
Oxford Response Stringency Index \citep{Hale2020}, which tracks the tightness of
non-pharmaceutical interventions. The index is shown for illustration of the NPIs, we
never use it directly. For legibility reasons, we transform the index so that lower
values represent higher levels of restrictions. A value of zero means all measures
incorporated in the index are turned on. The value 1 represents the situation in
mid-September, with restrictions on gatherings and public events, masking requirements,
but open schools and workplaces. In the seven weeks between mid September and early
November, cases increased by a factor of 10. Restrictions were somewhat tightened in
mid-October and again in early November. New infections remained constant throughout
November before rising again in December, prompting the most stringent lockdown to this
date. Schools and daycare centers were closed, so were customer-facing businesses except
for grocery and drug stores. From the peak of the second wave just before Christmas until
the trough in mid-February, newly detected cases decreased by almost three quarters. The
third wave in the spring of 2021 is associated with the B.1.1.7 strain, which became
dominant in March (Figure~\ref{fig:share_b117}) and stayed dominant for our entire
simulation period.\footnote{B.1.617.2 (Delta) reached Germany in April but still
accounted for less than 5\% of cases at the end of our simulation period.}
In early March, some NPIs were being relaxed; e.g., hairdressers and home improvement
stores were allowed to open again to the public. There were many changes in details of
regulations afterwards, but they did not change the overall stringency index.
